### 2018-11-20 articleSFDS.tex

Numerical experiments have become increasingly popular in many (if not all) industrial fields, as setting up field experiments can represent a huge investment for a company. Numerical simulations are generally considered as a substitute to bypass physical or field experiments \citep{santner2013,fang2005}. However, the complexity of the computer codes used in such simulations increases with the capacity of computer processors, and sometimes at a much higher rate. As a result, some codes have become greedy in computational time \citep{sacks1989}. Moreover, a gap between computer code outputs and field measures of the physical process that the code seeks to simulate is routinely observed. 
Checking the accuracy of the code by confronting it with field experiments is called validation \citep{bayarri2007}. This task is difficult since it is based on a few unavoidable field data and a computational code, often long to run. 
All along this paper, we will use the word ``code'' as a proxy for numerical code, sometimes also called numerical model, simulator or computational code and field experiment for real world experiment.
\newline

@@

The code generally depends on two kinds of inputs\hc variables and parameters.
The variables are input variables (observable and often controllable) which are set during a field experiment and can encompass environmental variables that can be measured.
The parameters are generally interpreted as physical constants defining the mathematical model of the system of interest, but can also contain so-called tuning parameters, which have no physical interpretation. They have to be set by the user to run the code and chosen carefully to make the code mimic the real physical phenomenon. 
The code can be mathematically represented by a function $f_c$. Let us note, in what follows, $\boldsymbol{\theta}\in\mathcal{Q}\subset\mathbb{R}^p$ to represent the parameter vector and $\mathbf{x}\in\mathcal{H}\subset \mathbb{R}^d$ for the variable vector. The space $\mathcal{Q}$ is called the input parameter space and $\mathcal{H}$ the input variable space.
The physical phenomenon is denoted by $\zeta$ and only depends on variables in vector $\boldsymbol{x}\in\mathcal{H}$, the parameter vector $\boldsymbol{\theta}$ having no counterpart in field experiments. \newline

A code output is then written as $f_c(\boldsymbol{x},\boldsymbol{\theta})$ whereas $\zeta(\boldsymbol{x})$ denotes the output of the physical phenomenon for the same variable $\boldsymbol{x}$. This is of course an idealized formalization, in which we assume that the code variables $\boldsymbol{x}$ are exhaustive to describe the phenomenon of interest, in the sense that the quantity to be predicted can take a single deterministic value $\zeta(\boldsymbol{x})$ for a given $\boldsymbol{x}$. 
In this paper, the quantity of interest is assumed to be a scalar but 
extensions with high dimension outputs are
possible \citep{higdon2008}. 
Therefore, in what follows, the outputs of $\zeta$ and $f_c$ lie in $\mathbb{R}$.
\newline

@@

Calibrating the code consists
in making the vector of parameters $\boldsymbol{\theta}$ consistent in some sense with these $n$ field data. In an industrial framework, uncertainty quantifications \citep{rocquigny2009quantifying} can be decomposed into a step by step procedure and calibration is identified as a key element of the so-called \textit{step B'}. As illustrated in \citet{damblin2015}, this step concerns calibration,
verification and validation (V\&V). V\&V can be further split into 3 phases  described in \citet{roache1998}, \citet{bayarri2007} and \citet{oberkampf1998}.
Calibration then aims at finding the "best" parameter vector $\boldsymbol{\theta}=\boldsymbol{\theta}^*$ such that the error term made by the
code in a statistical model is minimal. Several statistical modeling strategies have been proposed in the literature. When only measurement errors
are considered, \citet{cox2001} use a rather simple model, considering that the code does not differ from the phenomenon under study while
\citet{higdon2004}, \citet{kennedy2001} and \citet{bayarri2007} advocate for some extensions which encompass a \textit{model bias} 
or a \textit{model error} term, also dubbed as \textit{discrepancy} in the following. All of these models are reviewed and discussed in Section
\ref{sec:calibration}. The identifiability issues between the parameter $\boldsymbol{\theta}$ and the discrepancy were already discussed in the written discussions of \citet{kennedy2001}. \citet{tuo2015efficient} consider the calibration task as a minimization of a loss function between the code and the physical reality. 
In \citet{tuo2016theoretical}, they show that this loss function leads to an estimation of $\boldsymbol{\theta}$ depending on the chosen \textit{prior} distribution of the discrepancy. Then,  \citet{plumlee2017} advices an orthogonality 
specification for the discrepancy \textit{i.e.} the discrepancy should be orthogonal to the gradient of the computer code with respect to a loss function.
\newline

As an industrial illustrative example, we will focus, in this paper, on predicting the energy production from a photovoltaic (PV) plant \citep{martin2001}. The industrial context is to go through proposals as a manufacturer and a supplier for PV plants. The selling price announced by the industrial company has to be competitive enough to be successful in the bidding process. Of course, the building costs and the production over the plant lifetime have to be known to evaluate the profit margins. Although a best guess-estimate, the deterministic evaluation of PV production through a sophisticated computer code, does not fulfill the needs of a financial investor in  PV projects. To evaluate the financial risks of his/her investment and consequently to make his decision, the investor needs to assess the uncertainty around the expected production estimation. To do so, all the sources of uncertainties have to be identified and treated in their current form. Calibration will be useful for hunting down the uncertainties related to the modeling and quantify the range of the main potential errors made in predicting the profit ratio. \new{This real case study will allow us to emphasize the differences between the statistical models used for calibration in a context where the statistical hypotheses usually made are not guaranteed to be valid.}
\newline

@@

This paper first presents the illustrative case study (Section \ref{PVsection}). The stakes are given with the explanation of the code and the source of the experimental data. Section \ref{sec:calibration} deals with the presentation of the many different statistical models one can find in the literature which have been developed for calibration. Then, a highlight of the different likelihoods and conditional densities needed for parameter estimation is provided. In Section \ref{sec:application}, the different statistical models are implemented and tested for the PV application case, in order to illustrate the various ways of reasoning behind calibration and point out their differences.

@@

Today, the market in electricity production has become more and more competitive. Environmental issues have brought changes in such a way that producing electricity by exploiting sun-power has become a popular and a major vector of green production. However, building a PV plant represents a lot of financial risks. Indeed, many factors must be taken into account before computing the return rate. The overall building cost is the first figure needed but can easily be estimated. Once it is evaluated, a prediction of the PV plant production will set up the return rate. To compute such a prediction, a code has been developed, implementing a mathematical model which aims at reproducing the physical system of the plant. \newline

However, there are two major sources of uncertainty linked to this method. The first one is the meteorological data which we have difficulties to predict, especially in the changing environment due to global warming. In a project framework, we will usually use the meteorological data based on the previous years with past scenarios eventually adjusted to take into account temperature increase. The second source of uncertainties comes from the modeling errors. The code may encounter difficulties to mimic the physical system. As discussed above, this can be explained by the fact that the mathematical model implemented is only a simplified representation of the physical world, which might not take into account all the existing influent variables, and also depends on uncertain physical constants, which are precisely the parameters we wish to estimate. \newline

Consequently, the error made by the output of the code straightforwardly impacts the uncertainty on the estimation of production. In this article, we will focus only on the modeling errors. Practically these errors are responsible for one half ($4\%$) of the error made on the total energy given by the plant ($8\%$).

@@

To understand how the phenomenon has been coded, some explanation about how the PV cell works is needed. A PV cell is mainly composed of a semi-conductor material. For most technologies, this material is silicon \citep{luque2011}. The energy supply from the sun is remarkable at a quantum level. Indeed, the energy from the light spectrum will modify the energy levels of the silicon atoms until one electron appears. In a single crystal of semiconductor, two parts are visible. The ``p'' (positive) side which contains an excess of holes and the "n" side which contains an excess of electrons. A hole is an excess of a positive charge. The electron is by diffusion straightforwardly attracted to the hole, creating an electron/hole pair. The principle is to capture enough solar energy to create such an electron/hole pair. The displacement of an electron is directly  translated into electric current. The, so called, ``energy gap'', which has to be brought, corresponds to the difference between the energy of conduction band and the valence band. To create electricity, the incident solar ray on the PV cell has to have a spectrum energy higher than the energy gap. That is why, cloudy days are not favorable for PV plants production. The PV cell has a plastic film and a cover glass to protect the silicon. Otherwise, the lifetime of the cell would be too short because of its degradation. These protections act as a filter for the sun rays and some spectrum energy is lost. All in all, lots of conditions have to be met and only $20\%$ of the initial spectrum is at best transformed into electricity \citep{martin2001}. \newline

The code, hereafter considered as a ``black box'', is a solver of the main equations mimicking the electrical behavior of the PV plant. All along the article the code will represent a PV test stand with 12 panels connected together. The considered power will be the one before the inverter (multiplication of the continuous current and continuous voltage). Fortunately, for an in-depth exploration of the complete range of situations encountered in the domain of Bayesian calibration of computer codes, the ``black box'' code $f_c$ appears to be fast for the case study (one launch needs only $39\mu s$ to run). To investigate what happens when the code is time consuming, we will simply slow it down by restructuring the number of runs allowed for the computer code $f_c$. The code depends on some parameter vector $\boldsymbol{\theta}$ and input variables $\boldsymbol{x}$ detailed as follows (also called general inputs in \citet{plumlee2017}): $\boldsymbol{\theta}=\begin{pmatrix}
\eta \\
\mu_t \\
n_t \\
a_l \\
a_r\\
n_{inc}
\end{pmatrix}$ and $\boldsymbol{x}=\begin{pmatrix}
t\\
L\\
l\\
I_g\\
I_d \\
T_e
\end{pmatrix}$. \newline

The physical meaning of parameters is explained below \citep{duffie2013}\hc 
\begin{itemize}
\item $\eta$\hc module photo-conversion efficiency,
\item $\mu_t$\hc module temperature coefficient (the efficiency decreases when the temperature rises) in \%/°$C$,
\item $n_t$\hc reference temperature for the normal operating conditions of the module in °$C$,
\item $a_l$\hc reflection power of the ground (albedo),
\item $a_r$\hc describe the transmission of the radiation as a function of the incidence angle of solar rays, which depends on optical properties and the cleanliness,
\item $n_{inc}$\hc transmission factor for normal incidence. \newline
\end{itemize}

@@

Note that some temporal aspect is taken into account through the input variables. We do not consider any delay in the PV reaction to the forcing conditions. Time $t$ indicates here a snap shot corresponding to the instant when the power has to be computed. This code only focuses on a specific time and if the evolution of the power over a day is what we look for, a repetition over the specific duration has to be made. This operation has to consider the number of time steps available. For example, if $300$ configurations of $\boldsymbol{x}$ are accessible for one day, the code will have to be executed $300$ times to have the power evolution over a day. For the rest of the article, we will denote the code output referring to the i\textsuperscript{th} time step by $f_c(\boldsymbol{x}_i,\boldsymbol{\theta})$ and by $f_c(\textbf{X},\boldsymbol{\theta})$ the code outputs corresponding to the whole time frame contained in matrix $\textbf{X}$. \newline

A sensitivity analysis performed according to the screening method of Morris \citep{morris1991} has showed that only the variations of $\eta$, $\mu_t$ and $a_r$ have a significant impact on the power. This sensitivity analysis consists in evaluating with elementary displacements in a normalized input space, the impacts of these displacements on the output. To demonstrate that $\eta$, $\mu_t$ and $a_r$ have a significant impact over a whole duration but not instantaneously a PCA (Principal Component Analysis) is performed on all outputs generated for the duration and for all combinations of the design of experiments (DOE) of Morris. On the new uncorrelated basis of the space, the information is summed up by a new Morris plot. This representation allows us to visualize all the information summarized over the duration on one plot. However, to  implement such a method, the input space parameter needs to be well defined. That is why the work of the experts is really important. They have to define the range of each parameter as best as they can.\newline

@@

As mentioned above, the code represents a test stand of 12 panels. Data are available over 2 months and instantaneous power is collected every $10s$, which makes around $777,600$ points to process. Data are particularly treated when recording facilities are interrupted for some reasons. Figure \ref{fig:PowerExample} shows the kind of data collected from the stand over one month (on the left) and detailed for one day (on the right). Some days the production sticks to $0$. This typically happens when recording errors occur. Actually, the power saved is aberrant with too much high or 
negative power. Data cleaning allows to detect and sort these errors. On the right panel of Figure \ref{fig:PowerExample}, we can notice a typical behavior of an assembly of solar panels. When the irradiation of the sun is high, so is the production. As expected, the maximum production happens around noon when the irradiation is high.

@@

So far, experts are using the code with some parameter values with the knowledge that these parameters are uncertain (the so called reference values). They can also provide more expertise on the nature of the parameter. For example for $a_r$, the nominal value is $0.17$ and experts state that the parameter lies within the $95\%$ confidence interval $[0.05,0.29]$. We chose to consider $a_r$ as Gaussian with $a_r\sim\mathcal{N}(\mu=0.17,\sigma^2=3.6.10^{-3})$. The standard deviation is chosen equal to $0.06$ because we have considered the upper bound and the lower bound of the given interval as respectively the quantiles $a_{r_{0.975}}$ and $a_{r_{0.025}}$. Similarly, $\eta$ and $\mu_t$ are taken as Gaussian such as $\eta\sim\mathcal{N}(\mu=0.143,\sigma^2=2.5.10^{-3})$ and $\mu_t\sim\mathcal{N}(\mu=-0.4,\sigma^2=10^{-2})$. If $100$ realizations are drawn from the joint distribution of $\eta$, $\mu_t$ and $a_r$, the production curve and the \textit{prior} credibility interval can be simultaneously plotted on a same graph to see how uncertain the predicted power is over a day. Figure \ref{fig:ParamError} illustrates on the left the distribution of $\eta$, $\mu_t$ and $a_r$ and on the right the production curve obtained for reference values and the \prior credibility interval at $90\%$. On the right side, experiments collected that same day are also displayed. One can check that the \textit{prior} credibility interval, built thanks to the experts, looks coherent regarding the experimental data.\newline

@@

If one is interested in the energy produced rather than the power (the energy in $kWh$ is the power in $kW$ multiplied by a duration), one can easily compute the maximum and the minimum energy for say $100$ realizations. The energy for collected power is $W_{exp}=3.44 kWh$, the maximum energy computed $W_{max}=3.65 kWh$ and the minimum energy $W_{min}=2.93 kWh$. Straightforwardly $W_{min} < W_{exp} < W_{max}$ which means that the experts interval seems correct for that day. With the considered uncertainty on $\eta$, $\mu_t$ and $a_r$, the error made is about $20\%$ over only one day. 
Considering this error over a day, cumulative error over a lifetime plant could be too prejudicial. The aim of the calibration is to quantify this error and, at the same time, increase the knowledge on the parameter distribution. The results of calibration for this application case are detailed in Section \ref{sec:application}.

@@

Calibration intends to find the ``best fitting'' parameters of a computational code, in order to minimize the difference between the output and the experiments. \new{The variance of the measurement error is also unknown and has to be estimated as well as the parameters but will be considered as a nuisance parameter. It can be used in two cases.} In a forecasting context \citep{craig2001}, where the calibrated code on data collected on site can be used to compute the behavior of the power plant over the next time period. But also, in a prediction context, where data from an experimental stand are used to predict the behavior of a non-existing stand (assuming they have the same features). \newline

A simple way to express calibration is to write down a first and straightforward model. The computational code is set up to entirely replace the physical system. Intuitively, we can assume that $\forall \boldsymbol{x} \in \mathcal{H}, \zeta(\boldsymbol{x})=f_c(\boldsymbol{x},\boldsymbol{\theta})$ for some well-chosen $\boldsymbol{\theta}$, which leads to the following equation\hc

@@

The likelihood of such a model depends on $f_c$. In methods such as Maximum Likelihood Estimation (MLE) or as in Bayesian estimation (making recourse to many MCMC iterations), it becomes intractable to work with a time consuming $f_c$.\newline

For the sake of simplicity we will consider, in what follows, the code as deterministic. It means that for the same inputs, the output of the code is identical, which is generally the case. Even in a deterministic context, a gap between the code and the physical system is often unavoidable. This gap is called code error or discrepancy. Some papers advocate for adding this discrepancy in the statistical models \citep{kennedy2001,higdon2004,bayarri2007,bachoc2014}. In the following, we present three other models which take into account a time consuming code and/or an additional discrepancy.
\newline

@@

\noindent Let us consider a time consuming code. As said above, in this particular case, the computational burden become too huge to perform calibration. That is why, \citet{sacks1989} introduced an emulation of the, not yet computed, outputs from the code by a random function, \textit{i.e.} a stochastic process. The common choice is oriented toward the Gaussian process because the conditional Gaussian process is still a Gaussian process (see Appendix \ref{ap:GaussianProcesses} for more details). It is, parsimoniously, defined by its mean and covariance functions. The first ``simple'' and straightforward model was introduced by \citet{cox2001} which uses this emulation of $f_c$.

>>>>

Numerical experiments have become increasingly popular in many (if not all) industrial fields, as setting up field experiments can represent a huge investment for a company. Numerical simulations are generally considered as a substitute to bypass physical or field experiments \citep{santner2013,fang2005}. However, the complexity of the computer codes used in such simulations increases with the capacity of computer processors, and sometimes at a much higher rate. As a result, some codes have become greedy in computational time \citep{sacks1989}. Moreover, a gap between computer code outputs and field measures of the physical process that the code seeks to simulate is routinely observed. 
Checking the accuracy of the code by confronting it with field experiments is called validation \citep{bayarri2007}. This task is difficult since the requisite field data are scarce and it is based on a computational code that often has a long runtime. 
Throughout this paper, we will use the word ``code'' as a proxy for numerical code, sometimes also called numerical model, simulator or computational code and field experiment for real world experiment.
\newline

@@

The code generally depends on two kinds of inputs\hc variables and parameters.
The variables are input variables (observable and often controllable) which are set during a field experiment and can encompass environmental variables that can be measured.
The parameters are generally interpreted as physical constants defining the mathematical model of the system of interest, but can also contain so-called tuning parameters, which have no physical interpretation. They have to be set by the user to run the code and need to be chosen carefully to make the code mimic the real physical phenomenon. 
The code can be mathematically represented by a function $f_c$. Let us note, in what follows, $\boldsymbol{\theta}\in\mathcal{Q}\subset\mathbb{R}^p$ to represent the parameter vector and $\mathbf{x}\in\mathcal{H}\subset \mathbb{R}^d$ for the variable vector. The space $\mathcal{Q}$ is called the input parameter space and $\mathcal{H}$ the input variable space.
The physical phenomenon is denoted by $\zeta$ and only depends on variables in vector $\boldsymbol{x}\in\mathcal{H}$, the parameter vector $\boldsymbol{\theta}$ having no counterpart in field experiments. \newline

A code output is then written as $f_c(\boldsymbol{x},\boldsymbol{\theta})$ whereas $\zeta(\boldsymbol{x})$ denotes the output of the physical phenomenon for the same variable $\boldsymbol{x}$. This is of course an idealized formalization, in which we assume that the code variables $\boldsymbol{x}$ are exhaustive to describe the phenomenon of interest, in that the quantity to be predicted can take a single deterministic value $\zeta(\boldsymbol{x})$ for a given $\boldsymbol{x}$. 
In this paper, the quantity of interest is assumed to be a scalar but 
extensions with high dimension outputs are
possible \citep{higdon2008}. 
Therefore, in what follows, the outputs of $\zeta$ and $f_c$ lie in $\mathbb{R}$.
\newline

@@

Calibrating the code consists
in making the parameter vector $\boldsymbol{\theta}$ consistent in some sense with these $n$ field data. In an industrial framework, uncertainty quantifications \citep{rocquigny2009quantifying} can be decomposed into a step by step procedure and calibration is identified as a key element of the so-called \textit{step B'}. As illustrated in \citet{damblin2015}, this step concerns calibration,
verification and validation (V\&V). V\&V can be further split into 3 phases  described in \citet{roache1998}, \citet{bayarri2007} and \citet{oberkampf1998}.
Calibration then aims at finding the "best" parameter vector $\boldsymbol{\theta}=\boldsymbol{\theta}^*$ such that the error term made by the
code in a statistical model is minimal. Several statistical modeling strategies have been proposed in the literature. When only measurement errors
are considered, \citet{cox2001} use a rather simple model, considering that the code does not differ from the phenomenon under study while
\citet{higdon2004}, \citet{kennedy2001} and \citet{bayarri2007} advocate for some extensions which encompass a \textit{model bias} 
or a \textit{model error} term, also dubbed as \textit{discrepancy} in the following. All of these models are reviewed and discussed in Section
\ref{sec:calibration}. The identifiability issues between the parameter $\boldsymbol{\theta}$ and the discrepancy were already discussed in the written discussions of \citet{kennedy2001}. \citet{tuo2015efficient} consider the calibration task as a minimization of a loss function between the code and the physical reality. 
In \citet{tuo2016theoretical}, they show that this loss function leads to an estimation of $\boldsymbol{\theta}$ depending on the chosen \textit{prior} distribution of the discrepancy. Then,  \citet{plumlee2017} advises an orthogonality 
specification for the discrepancy \textit{i.e.} the discrepancy should be orthogonal to the gradient of the computer code with respect to a loss function.
\newline

As an industrial illustration, we will focus, in this paper, on predicting the energy production from a photovoltaic (PV) plant \citep{martin2001}. The industrial context is that of an electricity producer and supplier who has to consider bids from PV plants. The selling price announced by the industrial company has to be competitive enough to be successful in the bidding process. Of course, the building costs and the production over the plant lifetime have to be known to evaluate the profit margins. Although a best guess-estimate, the deterministic evaluation of PV production through a sophisticated computer code does not fulfill the needs of a financial investor in  PV projects. To evaluate the financial risks of the investment and consequently to make a decision, the investor needs to assess the uncertainty around the expected production estimation. To do so, all the sources of uncertainties have to be identified and treated in their current form. Calibration will be useful for hunting down the uncertainties related to the modeling and quantifying the range of the main potential errors made in predicting the profit ratio. \new{This real case study will allow us to emphasize the differences between the statistical models used for calibration in a context where the validity of the statistical hypotheses made is usually not guaranteed.}
\newline

@@

This paper first presents the illustrative case study (Section \ref{PVsection}). The issues at stake are described with the explanation of the code and the source of the experimental data. Section \ref{sec:calibration} deals with the presentation of the many different statistical models one can find in the literature which have been developed for calibration. Then, the different likelihoods and conditional densities needed for parameter estimation are highlighted. In Section \ref{sec:application}, the different statistical models are implemented and tested for the PV application case, in order to illustrate the various ways of reasoning behind calibration and point out their differences.

@@

The electricity production market has become increasingly competitive. Environmental issues have brought changes in such a way that producing electricity by exploiting solar power has become a popular and a major vector of green production. However, building a PV plant represents a considerable financial risk. Many factors must be taken into account before computing the return rate. The overall building cost is the first figure needed but can easily be estimated. Once it is evaluated, a prediction of the PV plant production will set up the return rate. To compute such a prediction, a code has been developed, implementing a mathematical model which aims at reproducing the physical system of the plant. \newline

However, there are two major sources of uncertainty linked to this method. The first one is the meteorological data which are difficult to predict, especially in an environment that is changing due to global warming. In a project framework, we will usually use the meteorological data based on the previous years with past scenarios adjusted if necessary to take into account the temperature increase. The second source of uncertainties comes from the modeling errors. The code may encounter difficulties in mimicking the physical system. As discussed above, this can be explained by the fact that the mathematical model implemented is only a simplified representation of the physical world, which might not take into account all the existing influential variables, and also depends on uncertain physical constants, which are precisely the parameters we wish to estimate. \newline

Consequently, the error made by the output of the code directly impacts the uncertainty on the estimation of production. In this article, we will focus only on the modeling errors. In practice, these errors are responsible for one half ($4\%$) of the error made on the total energy given by the plant ($8\%$).

@@

To understand how the phenomenon has been coded, some explanation about how the PV cell works is needed. A PV cell is mainly composed of a semi-conductor material. For most technologies, this material is silicon \citep{luque2011}. The energy supply from the sun is remarkable at a quantum level since the energy from the light spectrum will modify the energy levels of the silicon atoms until one electron appears. In a single semiconductor crystal, two parts are visible. The ``p'' (positive) side which contains an excess of holes and the "n" side which contains an excess of electrons. A hole is an excess of a positive charge. The electron is attracted to the hole by diffusion, creating an electron/hole pair. The principle is to capture enough solar energy to create such an electron/hole pair. The displacement of an electron is directly  translated into electric current. The so called ``energy gap'' corresponds to the difference between the energy of the conduction band and the valence band. To create electricity, the incident solar ray on the PV cell has to have an energy spectrum higher than the energy gap. That is why cloudy days are not favorable for PV plant production. The PV cell has a plastic film and a glass cover to protect the silicon. Otherwise, the lifetime of the cell would be too short because of its degradation. These protections act as a filter for the sun's rays and some of the energy spectrum is lost. All in all, many conditions have to be met and only $20\%$ of the initial spectrum is at best transformed into electricity \citep{martin2001}. \newline

The code, hereafter considered as a ``black box'', is a solver of the main equations mimicking the electrical behavior of the PV plant. In this article the code will represent a PV test stand with 12 panels connected together. The power considered will be the one before the inverter (multiplication of the continuous current and continuous voltage). Fortunately, for an in-depth exploration of the complete range of situations encountered in the domain of Bayesian calibration of computer codes, the ``black box'' code $f_c$ appears to be fast for the case study (one launch needs only $39\mu s$ to run). To investigate what happens when the code is time consuming, we will simply slow it down by restructuring the number of runs allowed for the computer code $f_c$. The code depends on some parameter vector $\boldsymbol{\theta}$ and input variables $\boldsymbol{x}$ detailed as follows (also called general inputs in \citet{plumlee2017}): $\boldsymbol{\theta}=\begin{pmatrix}
\eta \\
\mu_t \\
n_t \\
a_l \\
a_r\\
n_{inc}
\end{pmatrix}$ and $\boldsymbol{x}=\begin{pmatrix}
t\\
L\\
l\\
I_g\\
I_d \\
T_e
\end{pmatrix}$. \newline

The physical meaning of the parameters is explained below \citep{duffie2013}\hc 
\begin{itemize}
\item $\eta$\hc module photo-conversion efficiency,
\item $\mu_t$\hc module temperature coefficient (the efficiency decreases when the temperature rises) in \%/°$C$,
\item $n_t$\hc reference temperature for the normal operating conditions of the module in °$C$,
\item $a_l$\hc reflection power of the ground (albedo),
\item $a_r$\hc transmission of the radiation as a function of the incidence angle of solar rays, which depends on optical properties and the cleanliness,
\item $n_{inc}$\hc transmission factor for normal incidence. \newline
\end{itemize}

@@

Note that the temporal aspect is taken into account to a certain extent through the input variables. We do not consider any delay in the PV reaction to the forcing conditions. Time $t$ indicates here a snap shot corresponding to the instant when the power has to be computed. This code only focuses on a specific time and if the evolution of the power over a day is what we look for, a repetition over the specific duration has to be made. This operation has to consider the number of time steps available. For example, if $300$ configurations of $\boldsymbol{x}$ are accessible for one day, the code will have to be executed $300$ times to obtain the power evolution over a day. For the rest of the article, we will denote the code output referring to the i\textsuperscript{th} time step by $f_c(\boldsymbol{x}_i,\boldsymbol{\theta})$ and by $f_c(\textbf{X},\boldsymbol{\theta})$ the code outputs corresponding to the whole time frame contained in matrix $\textbf{X}$. \newline

A sensitivity analysis performed according to the screening method of Morris \citep{morris1991} showed that only the variations of $\eta$, $\mu_t$ and $a_r$ have a significant impact on the power. This sensitivity analysis consists in evaluating with elementary displacements in a normalized input space, the impacts of these displacements on the output. To demonstrate that $\eta$, $\mu_t$ and $a_r$ have a significant impact over a whole duration but not instantaneously a PCA (Principal Component Analysis) is performed on all outputs generated for the duration and for all combinations of the design of experiments (DOE) of Morris. On the new uncorrelated basis of the space, the information is summed up by a new Morris plot. This representation makes it possible to visualize all the information summarized over the duration on one plot. However, to  implement such a method, the input space parameter needs to be well defined. That is why the work of the experts is extremely important. They have to define the range of each parameter as best they can.\newline

@@

As mentioned above, the code represents a test stand of 12 panels. Data are available over 2 months and instantaneous power is collected every $10s$, which makes around $777,600$ points to process. When the recording facilities are interrupted for some reason, a specific data processing is carried out. Figure \ref{fig:PowerExample} shows the kind of data collected from the stand over one month (on the left) and detailed for one day (on the right). On certain days the production remains stuck at $0$. This typically happens when recording errors occur. In fact, the power saved is aberrant with too much high or 
negative power. These errors can be detected and sorted by data cleaning. The panel on the right in Figure \ref{fig:PowerExample} shows the typical behavior of an assembly of solar panels. When the irradiation of the sun is high, so is the production. As expected, the maximum production happens around noon when the irradiation is high.

@@

So far, experts have used the code with some parameter values with the knowledge that these parameters are uncertain (the so called reference values). They can also provide more expertise on the nature of the parameter. For example for $a_r$, the nominal value is $0.17$ and experts state that the parameter lies within the $95\%$ confidence interval $[0.05,0.29]$. We chose to consider $a_r$ as Gaussian with $a_r\sim\mathcal{N}(\mu=0.17,\sigma^2=3.6.10^{-3})$. The standard deviation is chosen equal to $0.06$ because we considered the upper bound and the lower bound of the given interval as respectively the quantiles $a_{r_{0.975}}$ and $a_{r_{0.025}}$. Similarly, $\eta$ and $\mu_t$ are taken as Gaussian such that $\eta\sim\mathcal{N}(\mu=0.143,\sigma^2=2.5.10^{-3})$ and $\mu_t\sim\mathcal{N}(\mu=-0.4,\sigma^2=10^{-2})$. If $100$ realizations are drawn from the joint distribution of $\eta$, $\mu_t$ and $a_r$, the production curve and the \textit{prior} credibility interval can be simultaneously plotted on the same graph to see how uncertain the predicted power is over a day. Figure \ref{fig:ParamError} illustrates on the left the distribution of $\eta$, $\mu_t$ and $a_r$ and on the right the production curve obtained for reference values and the \prior credibility interval at $90\%$. On the right side, experiments collected that same day are also displayed. Figure \ref{fig:ParamError} shows that the \textit{prior} credibility interval, built thanks to the experts, looks coherent with respect to the experimental data.\newline

@@

If one is interested in the energy produced rather than the power (the energy in $kWh$ is the power in $kW$ multiplied by a duration), one can easily compute the maximum and the minimum energy for say $100$ realizations. The energy for collected power is $W_{exp}=3.44 kWh$, the maximum energy computed $W_{max}=3.65 kWh$ and the minimum energy $W_{min}=2.93 kWh$. $W_{min} < W_{exp} < W_{max}$ which means that the experts' interval seems correct for that day. With the considered uncertainty on $\eta$, $\mu_t$ and $a_r$, the error made is about $20\%$ over only one day. 
Considering this error over a day, the cumulative error over the lifetime of a plant could be too prejudicial. The aim of the calibration is to quantify this error and, at the same time, increase the knowledge on the parameter distribution. The calibration results for this application case are detailed in Section \ref{sec:application}.

@@

Calibration aims to find the ``best fitting'' parameters of a computational code, in order to minimize the difference between the output and the experiments. \new{The variance of the measurement error is also unknown and has to be estimated as well as the parameters but will be considered as a nuisance parameter. It can be used in two cases.} In a forecasting context \citep{craig2001}, where the code calibrated on data collected on site can be used to compute the behavior of the power plant over the next time period. But also, in a prediction context, where data from an experimental stand are used to predict the behavior of a non-existing stand (assuming they have the same features). \newline

A simple way to express calibration is to write down a first simple model. The computational code is set up to entirely replace the physical system. Intuitively, we can assume that $\forall \boldsymbol{x} \in \mathcal{H}, \zeta(\boldsymbol{x})=f_c(\boldsymbol{x},\boldsymbol{\theta})$ for some well-chosen $\boldsymbol{\theta}$, which leads to the following equation\hc

@@

The likelihood of such a model depends on $f_c$. In methods such as Maximum Likelihood Estimation (MLE) or Bayesian estimation (which resorts to many MCMC iterations), it becomes intractable to work with a time consuming $f_c$.\newline

For the sake of simplicity we will consider the code as deterministic in what follows. It means that for the same inputs, the output of the code is identical, which is generally the case. Even in a deterministic context, a gap between the code and the physical system is often unavoidable. This gap is called code error or discrepancy. Some papers advocate adding this discrepancy to statistical models \citep{kennedy2001,higdon2004,bayarri2007,bachoc2014}. In the following, we present three other models which take into account a time consuming code and/or an additional discrepancy.
\newline

@@

\noindent Let us consider a time consuming code. As said above, in this particular case, the computational burden become too huge to perform calibration. That is why \citet{sacks1989} introduced an emulation of the, not yet computed, outputs from the code by a random function, \textit{i.e.} a stochastic process. The common choice is a Gaussian process because the conditional Gaussian process is still a Gaussian process (see Appendix \ref{ap:GaussianProcesses} for more details). It is, parsimoniously, defined by its mean and covariance functions. The first ``simple'' model was introduced by \citet{cox2001} which uses this emulation of $f_c$.

\begin{eqnarray}
\mathcal{M}_2 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i} &=& F(\boldsymbol{x}_i,\boldsymbol{\theta}) + \epsilon_i,
\label{eq:M2}\\
F(\bullet,\bullet) & \sim &{\mathcal{GP}}{\Big(m_S(\bullet,\bullet),c_S\{(\bullet,\bullet),(\bullet,\bullet)\}\Big)},
\nonumber
\end{eqnarray}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$ and the random function $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ stands for a Gaussian process (GP) over the joint domain of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. \new{For the following, we consider that the measurement error is independent on the error made by the Gaussian process}. The mean function $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ is generally a linear form of simple functions of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its covariance function $c_S\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}=\sigma_S^2 r_{\boldsymbol{\psi}_S}\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}$ is such that the function $r_{\boldsymbol{\psi_S}}\{(\bullet,\bullet),(\bullet,\bullet)\}$ is the correlation function with a parameter vector $\boldsymbol{\psi}_S$. This parameter vector represents the scale and the regularity of the kernel and where $\sigma_S^2$ represents the variance. The mean $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ can be written as\newline
